Sequential algorithms to split and merge ultra-high resolution 3D images

### 2017-07-27 paper.tex
Integrated multiple writes in paper

>>>>

\subsubsection{Multiple writes}
\begin{figure}[h]
  \centering
  \includegraphics[width=0.45\columnwidth]{figures/benchmark-mwrites/mwrites-comparision-ssd.pdf}
  \hfill
  \includegraphics[width=0.45\columnwidth]{figures/benchmark-mwrites/mwrites-comparision-hdd.pdf}\\
  \includegraphics[width=0.45\columnwidth]{figures/benchmark-mwrites/mwrites-breakdown-ssd.pdf}
  \hfill
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-mwrites/mwrites-breakdown-hdd.pdf}
  \caption{Comparison between Multiple writes, blocks and slices. Left column: SSD. Right column: HDD. Top row: overall merging time. Bottom row: breakdown by read, write and seek time.}
  % Gnuplot file: scripts/blocks-slices/createboxplot.gnplt
\label{fig:multiple-writes}
\end{figure}
